### 2019-12-02 Mathematical Statistics/04_sampling_distributions.rmd
ms refactor
ms refactor

```{r, echo = T, fig.height=3.5, fig.width=8}
pdf <- function(x) (3/16)*(x - 4)^2
x <- seq(from = 2, to = 6, by = 0.001)
y <- pdf(x)

@@

Use the CLT approximation with continuity correction, and compare with the exact probility.

>>>>

```{r, echo = T, fig.height=2.6, fig.width=8}
pdf <- function(x) (3/16)*(x - 4)^2
x <- seq(from = 2, to = 6, by = 0.001)
y <- pdf(x)

@@

Use the CLT approximation with continuity correction, and compare with the exact probability.
